%**********************************************************************

% right side/flush
\chapterend

\begin{titlepage}

\begin{otherlanguage}{english} 
\begin{abstract} % Abstract

Although Cryptocurrencies are gaining more and more importance in the modern world, it is mostly as a simple digital currency. However, with most of the digital coins you can do much more than simply pay for something. Ethereum is a perfect example for this.

Ethereum has an implementation which called Smart Contracts and they are just that. Smart Contracts allow the creator to define rules and conditions to distribute coins directly in the Blockchain of the Cryptocurrency since a Smart Contract is simply custom Code which gets executed if User interacts with it.

To explore the possibilities of Smart Contracts a demo \ac{DApp} was created in the form of a Lottery. Especially with Lotteries there is always the problem that a trustworthy person or organization has to hold the money until the drawings and later pay the winners correctly. 

With a Smart Contract all this becomes unnecessary because the Contract itself holds the coins on the Blockchain until the drawing and then every user can withdraw their winnings theirselfs. Moreover, the Smart Contract itself is also public and the Source Code can be read by anybody with basic porgramming skills, to check under which conditions the coins go from wallet A to wallet B.

\end{abstract}
\end{otherlanguage}


\end{titlepage}

%**********************************************************************
